---
title: "GW Assignment - Biden Transition"
author: "Jacob Liedke"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(janitor)
library(scales)
library(gt)
library(kableExtra)
options(dplyr.summarise.inform = FALSE)
library(dplyr)

#run the script for step 03 to update the datasets to capture the current live verions
#and load all the new dataset objects into the environment (you'll see them populate on the upper right window)
source("03_compare_current_with_previous.R")

```

**Note: use either kable/kableExtra or gt tables to format your final tables for the questions below. You'll likely find it easier to figure out the data parts first, then once that's done add the table formatting.**

# AGENCY TEAMS

Come up with the necessary R code to return the following for the agency review teams.

### *New Names*

Below write code to show the new names added to the agency review team lists since the prior data provided.  
  

```{r, echo=FALSE}
myurl <- "https://buildbackbetter.gov/the-transition/agency-review-teams/"
website1 <- GET(myurl) 
tbls <- html_nodes(content(website1), "table")
num_tables <- length(tbls)
num_tables


scrape_table <- function(tablenum) {

  url <- "https://buildbackbetter.gov/the-transition/agency-review-teams/"
  website1 <- GET(url) 
  titles <- html_nodes(content(website1), "h2")
  title1 <- print(html_text(titles)[[tablenum]])
  table1 <- html_table(tbls[[tablenum]], fill=TRUE)
  table1 <- table1 %>% 
    as_tibble() %>% 
    clean_names() %>% 
    mutate(
      agency = title1
    ) %>% 
    select(agency, everything())
  
  return(table1)

}

scrape_table(1)

num_tables

num_sequence <- seq(1, num_tables)
num_sequence

transition_data_scraped <- map_df(num_sequence, scrape_table)

transition_data_scraped

transition_data_scraped <- transition_data_scraped %>% 
  mutate(
    idstring = str_trim(paste0(name, most_recent_employment, agency)),
    namestring = str_trim(paste0(name, most_recent_employment))
  )

multiplenames <- transition_data_scraped %>% 
  count(namestring) %>% 
  filter(n > 1) %>% 
  pull(namestring)

transition_data_scraped <- transition_data_scraped %>% 
  mutate(
    on_multiple_teams = if_else(namestring %in% multiplenames, "Y", "")
  )

transition_data_scraped <- transition_data_scraped %>% 
  mutate(
    team_lead = if_else(str_detect(name, "Team Lead"), "Y", ""),
    name = str_remove(name, ", Team Lead")
  ) %>% 
  select(agency, name, team_lead, on_multiple_teams, everything())

saveRDS(transition_data_scraped, "processed_data/transition_data_scraped.rds")

current_transition <- readRDS("processed_data/transition_data_scraped.rds")
current_transition

previous_transition <- readRDS("archived_data/transition_data_archived_2020_11_24t09_52.rds")
previous_transition

new_transition_names <- anti_join(current_transition, previous_transition, by = "idstring")
new_transition_names %>%
   kbl(caption = "New transition names") %>%
    kable_classic(full_width = F, html_font = "Cambria")

 

```


### *Aggregate Team Changes*

Add data to show the total number of people appointed to each agency team, along with change since last time reflecting the number of new people added. Omit agencies with no change at all.  
  

```{r, echo=FALSE}

count_current_agencies <- current_transition %>%
  count(agency, name = "current_agency_count")
  count_current_agencies %>%

count_previous_agencies <- previous_transition %>%
  count(agency,name = "previous_agency_count")
count_previous_agencies

count_compare_agencies <- left_join(count_current_agencies, count_previous_agencies, by = "agency")
count_compare_agencies
count_difference_agencies <- count_compare_agencies %>% 
  mutate(
    change = current_agency_count - previous_agency_count
  )

# number of changes by department
count_difference_agencies[count_difference_agencies$change != 0, ] %>%
   kbl(caption = "Count of current agencies") %>%
    kable_classic(full_width = F, html_font = "Cambria")

## number of changes by department in descending order
count_difference_agencies[count_difference_agencies$change != 0, ] %>%
  arrange(desc(change)) %>%
   kbl(caption = "Count of current agencies") %>%
    kable_classic(full_width = F, html_font = "Cambria")

```


### *Largest and Smallest Overall*

Show the top 10 **largest** agency review teams as of today:

```{r, echo=FALSE}

count_current_agencies %>%
  arrange(desc(current_agency_count
)) %>%
  slice(1:10) %>%
  kbl(caption = "10 largest agency review teams") %>%
  kable_classic(full_width = F, html_font = "Cambria")


```

Show the top **smallest** agency review teams as of today - which we'll define here as less than five members:

```{r, echo=FALSE}

count_current_agencies %>%
  filter(current_agency_count < 5) %>%
  arrange(desc(current_agency_count
)) %>%
  kbl(caption = "Smallest agency review teams (< 5)") %>%
  kable_classic(full_width = F, html_font = "Cambria")
 

```



# WHITE HOUSE SENIOR STAFF

Come up with the necessary R code to return the following for the WH senior staff.

### *New Names*

Below write code to show the new names added to the senior staff lists since the prior data provided.  
  

```{r, echo=FALSE}
## Dec 8 vs Nov 24 
current_senior_staff <- readRDS("processed_data/staff_data_scraped.rds")
current_senior_staff
previous_senior_staff <- readRDS("archived_data/staff_data_archived_2020_11_24t14_00.rds")
previous_senior_staff

new_senior_staff_names <- anti_join(current_senior_staff, previous_senior_staff, by = "idstring")
new_senior_staff_names

new_senior_staff_names %>%
  kbl(caption = "New senior staff members") %>%
  kable_classic(full_width = F, html_font = "Cambria")


 

```


### *Total Number of Current vs. Previous*

Add code to show the total number of people currently named to the WH senior staff, vs. the previous total number.  
  

```{r, echo=FALSE}

n_previous_staff <- count(previous_senior_staff) %>%
   kbl(caption = "Number of senior staff members previously") %>%
  kable_classic(full_width = F, html_font = "Cambria")
n_current_staff <- count(current_senior_staff) %>%
   kbl(caption = "Number of senior staff members currently") %>%
  kable_classic(full_width = F, html_font = "Cambria")
n_previous_staff
n_current_staff



```
